### 2014-04-22 docs/paper/paper.tex
robot closed loop diagram

% FIXME small diagram of hypothetical system in the loop (UI, robot, hardware, etc.)

@@

Both the input and output channels are transport-agnostic and can be attached to application-specific custom hardware that allows for
I/O to be performed over the desired interface, such as Ethernet. The implemented design performs I/O over Gigabit Ethernet using a custom Ethernet frame format for efficiency.

@@

% FIXME citation about why 2D is ``good enough''
As only one-dimensional and two-dimensional population units have been implemented, networks that require populations to compute functions
of three or more independent variables cannot be simulated with this design.
However, the majority of existing models in Nengo do not use populations with more than two input dimensions.
A controlled oscillator is an example of a kind of NEF network that cannot be simulated in our hardware implementation,
because it requires the approximation of a three-dimensional nonlinear function. Our implementation can simulate higher-dimensional representations
by simulating dimensions individually or in pairs, as long as each approximated function is either linear or is nonlinear in only one or two dimensions.

>>>>

@@

Both the input and output channels are transport-agnostic and can be attached to application-specific custom hardware that allows for
I/O to be performed over the desired interface, such as Ethernet. The implemented design performs I/O over Gigabit Ethernet using a custom Ethernet frame format for efficiency.
Input and output channels could also be implemented for sensors and actuators to allow for autonomous operation of a Nengo network in hardware once it has been sent to the board
(Figure~\ref{fig:closedloop}).

\includegraphics[width=5.0in]{robot-closed-loop.eps}

\caption{Block diagram of a high-level closed-loop autonomous system using \design{}.}
\label{fig:closedloop}
\end{figure}

@@

As only one-dimensional and two-dimensional population units have been implemented, networks that require populations to compute functions
of three or more independent variables cannot be simulated with this design.
However, the majority of existing models in Nengo do not use populations with more than two input dimensions.
A controlled oscillator is an example of a kind of NEF network that cannot be simulated in our hardware implementation,
because it requires the approximation of a three-dimensional nonlinear function. Our implementation can simulate higher-dimensional representations
by simulating dimensions individually or in pairs, as long as each approximated function is either linear or is nonlinear in only one or two dimensions.
